---
title: "UNIT_2_Assignment"
author: "sindhu"
date: "2024-08-02"
output: html_document
---



```{r}
library(ISLR)
library(MASS)
```

```{r}
?Boston
```

```{r}
data("Boston")
```


```{r}
boston=Boston

```


#### 1) In this exercise you will create some simulated data and will fit simple linear regression models to it. Make sure to use set.seed(1) prior to starting part (a) to ensure consistent results.rnorm


```{r}

set.seed(1)
x=rnorm(100,mean = 0,sd=1)
x

eps=rnorm(100,mean=0,sd=sqrt(0.25))
eps

y = -1+0.5*x+eps
```


```{r}
y
length(y)
```
beta 0 is -1
beta 1 is 0.5


```{r}

plot(x,y)
```
there is a positive linear relation ship between x and y.

```{r}

model_6=lm(y~x)
model_6
```


```{r}
summary(model_6)
```
 both are same estimated and actual beta 0 and beta 1 


```{r}

plot(x,y)
abline(model_6,col="red",lwd=3,lty=6)
abline(coef = c(-1,0.5),col="blue",lwd=2)
legend("topleft",c("LR","PR"),col=c("red","blue"),lty=c(6,1),lwd=c(3,2))
```

#### 2)This problem involves the “Boston” data set, which we saw in the lab for this chapter. We will now try to predict per capita crime rate using the other variables in this data set. In other words, per capita crime rate is the response, and the other variables are the predictors.



```{r}

Assign_2_1=lm(crim~zn,data = boston)
summary(Assign_2_1)
```
```{r}
plot(boston$zn,boston$crim)
```


* there is relationship between per captia crime rate and zn, but that is negative relationship

```{r}
Assign_2_2=lm(crim~indus,data = boston)
summary(Assign_2_2)
```
```{r}
plot(boston$indus,boston$crim)
```
.

```{r}
Assign_2_3=lm(crim~chas,data = boston)
summary(Assign_2_3)
```

```{r}
plot(boston$chas,boston$crim)
```

```{r}
Assign_2_4=lm(crim~nox,data = boston)
summary(Assign_2_4)
```

```{r}
plot(boston$nox,boston$crim)
```



```{r}
Assign_2_5=lm(crim~rm,data = boston)
summary(Assign_2_5)
```

```{r}
plot(boston$rm,boston$crim)
```



```{r}
Assign_2_6=lm(crim~age,data = boston)
summary(Assign_2_6)
```

```{r}
plot(boston$age,boston$crim)
```


```{r}
Assign_2_7=lm(crim~dis,data = boston)
summary(Assign_2_7)
```

```{r}
plot(boston$dis,boston$crim)
```


```{r}
Assign_2_8=lm(crim~rad,data = boston)
summary(Assign_2_8)
```

```{r}
plot(boston$rad,boston$crim)
```


```{r}
Assign_2_9=lm(crim~tax,data = boston)
summary(Assign_2_9)
```

```{r}
plot(boston$tax,boston$crim)
```


```{r}
Assign_2_10=lm(crim~ptratio,data = boston)
summary(Assign_2_10)
```

```{r}
plot(boston$ptratio,boston$crim)
```


```{r}
Assign_2_11=lm(crim~black,data = boston)
summary(Assign_2_11)
```

```{r}
plot(boston$black,boston$crim)
```


```{r}
Assign_2_12=lm(crim~lstat,data = boston)
summary(Assign_2_12)
```

```{r}
plot(boston$lstat,boston$crim)
```


```{r}
Assign_2_13=lm(crim~medv,data = boston)
summary(Assign_2_13)
```

```{r}
plot(boston$medv,boston$crim)
```




```{r}

Assign_2_b=lm(crim~.,data = boston)
summary(Assign_2_b)
```





